Personal Total Income of Individual in the United States of America in 2023

### 2024-10-25 paper/paper.qmd
Change the position of title of tables in Model

::: {#tbl-coefficients}
**Table 1: Coefficients from the Linear Regression Model**

@@

::: {#tbl-VIF}
**Table 2: Variance Inflation Factors (VIF) for Predictor Variables**

@@

::: {#tbl-modelperformance}
**Table 3: Model Performance Metrics**

@@

::: {#tbl-randomforestMSE}
**Table 4: Best Random Forest Model Performance Metrics**

@@

::: {#tbl-randomforestimportance}
**Table 5: Feature Importance in the Best Random Forest Model**

@@

::: {#tbl-XGBoostMSE}
**Table 6: XGBoost Model Performance Metrics**

@@

::: {#tbl-XGBoostCV}
**Table 7: XGBoost Cross-Validation Performance**

>>>>

::: {#tbl-coefficients}
\begin{center}
Table 1: Coefficients from the Linear Regression Model
\end{center}

@@

::: {#tbl-VIF}
\begin{center}
Table 2: Variance Inflation Factors (VIF) for Predictor Variables
\end{center}

@@

::: {#tbl-modelperformance}
\begin{center}
Table 3: Model Performance Metrics
\end{center}

@@

::: {#tbl-randomforestMSE}
\begin{center}
Table 4: Best Random Forest Model Performance Metrics
\end{center}

@@

::: {#tbl-randomforestimportance}
\begin{center}
Table 5: Feature Importance in the Best Random Forest Model
\end{center}

@@

::: {#tbl-XGBoostMSE}
\begin{center}
Table 6: XGBoost Model Performance Metrics
\end{center}

@@

::: {#tbl-XGBoostCV}
\begin{center}
Table 7: XGBoost Cross-Validation Performance
\end{center}
